API design for machine learning software: experiences from the scikit-learn project

### 2013-06-24 paper.tex
update my affiliation

\author{Lars~Buitinck~\inst{1} \and
        Gilles~Louppe~\inst{2} \and
        Mathieu~Blondel~\inst{3} \and
        Fabian~Pedregosa~\inst{4} \and
        Andreas~Mueller~\inst{5} \and
        Olivier~Grisel~\inst{6} \and
        Vlad~Niculae~\inst{7} \and
        Peter~Prettenhofer~\inst{8} \and
        Alexandre~Gramfort~\inst{9} \and
        Jacques~Grobler~\inst{4} \and
        Robert~Layton~\inst{10} \and
        Jake~Vanderplas~\inst{11} \and
        Arnaud~Joly~\inst{2} \and
        Brian Holt~\inst{12} \and
        Gaël~Varoquaux~\inst{4}}

\institute{University of Amsterdam \and
           University of Liège \and
           Kobe University \and
           Parietal, INRIA Saclay \and
           University of Bonn \and
           Nuxeo \and 
           University of Bucharest \and
           Bauhaus-Universitat \and
           Telecom ParisTech \and
           University of Ballarat \and
           University of Washington \and
           Samsung Electronics Research Institute}

>>>>

\author{Lars~Buitinck~\inst{1} \and
        Gilles~Louppe~\inst{2} \and
        Mathieu~Blondel~\inst{3} \and
        Fabian~Pedregosa~\inst{4} \and
        Andreas~Mueller~\inst{5} \and
        Olivier~Grisel~\inst{6} \and
        Vlad~Niculae~\inst{7} \and
        Peter~Prettenhofer~\inst{8} \and
        Alexandre~Gramfort~\inst{4,9} \and
        Jacques~Grobler~\inst{4} \and
        Robert~Layton~\inst{10} \and
        Jake~Vanderplas~\inst{11} \and
        Arnaud~Joly~\inst{2} \and
        Brian Holt~\inst{12} \and
        Gaël~Varoquaux~\inst{4}}

\institute{Informatics Institute, University of Amsterdam \and
           University of Liège \and
           Kobe University \and
           Parietal, INRIA Saclay \and
           University of Bonn \and
           Independent consultant \and
           University of Bucharest \and
           Ciuvo GmbH \and
           Institut Mines-Telecom, Telecom ParisTech, CNRS LTCI \and
           University of Ballarat \and
           University of Washington \and
           Samsung Electronics Research Institute}
